\documentclass{resume}

\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Riley Francis}
\address{Storrs, CT \\ +1 (860) 481-1411}
\address{
\href{mailto:riley.francis@uconn.edu}{riley.francis@uconn.edu} \\
\href{https://www.linkedin.com/in/rileyfrancis314}{https://linkedin.com/in/rileyfrancis314} \\
\href{https://rileyfrancis.github.io}{https://rileyfrancis.github.io}
}

\begin{document}

%----------------------------------------------------------------------------------------
% EDUCATION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
    {\bf University of Connecticut}, Storrs, CT \hfill Aug 2023 -- Expected May 2027 \\
    Dual Degree: {\it BS Computer Science, BA Pure Mathematics} \\
    Honors Program, Honors Scholar, COE Dean's List, CLAS Dean's List \\
    GPA: 3.921 / 4.000

    {\bf University of Edinburgh}, Edinburgh, Scotland \hfill Jan 2025 -- May 2025 \\
    Visiting Student, School of Informatics \\
    Study Abroad for Spring 2025 semester

    {\bf Summer Field Ecology Program}, Limpopo Province, South Africa \hfill May 2024 -- Jun 2024 \\
    UConn Study Abroad Program focused on ecological systems, society, and social rights issues
\end{rSection}

%----------------------------------------------------------------------------------------
% EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}
    \textbf{Student Computer Programming Specialist} \hfill Apr 2023 -- Present \\
    University of Connecticut, Storrs, CT
    \begin{itemize}
        \itemsep -4pt
        \item Handle redistribution and disposal of university electronic equipment.
        \item Configure and troubleshoot Windows, macOS, and Linux devices for reuse.
    \end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
% PROJECTS & RESEARCH
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects \& Research}
    \textbf{Reinforcement Learning on Autonomous Robots Inside Meta's Habitat-Lab} \hfill Feb 2021 -- Jan 2023 \\
    Storrs, CT \\
    Mentor: Dr. Jonathan Shihao Ji
    \begin{itemize}
        \itemsep -4pt
        \item Developed a reinforcement learning method for training legged robots (i.e. \href{https://bostondynamics.com/products/spot/}{Spot}) inside Meta's Habitat-Lab.
        \item Collaborated in a team of four other researchers.
        \item Formulated a research paper discussing our results. Paper available upon request.
    \end{itemize}

    \textbf{Convolutional Neural Network for Classifying ASL Letters.} \hfill Aug 2025 -- Dec 2025 \\
    Storrs, CT
    \begin{itemize}
        \itemsep -4pt
        \item Developed a Convolutional Neural Network (CNN) capable of classifying American Sign Language letters.
        \item Documented my work in GitHub and in a written report. \url{https://tinyurl.com/48jtrf9a}
    \end{itemize}

    \textbf{Interpreting GNNs with MIPExplainer: Explanations for Alzheimer’s and Autism} \hfill May 2025 -- Jul 2025 \\
    Greensboro, NC \\
    Mentor: Dr. Chunjiang Zhu
    \begin{itemize}
        \itemsep -4pt
        \item Applied MIPExplainer to graph neural networks to identify brain-region features influencing Alzheimer's and Autism prediction.
        \item Produced sparse model-level explanations to highlight key connectivity structures. Paper available upon request.
    \end{itemize}

    \textbf{Wagner-Fischer Spellcheck Algorithm Video} \hfill Aug 2024 -- Dec 2024 \\
    Storrs, CT
    \begin{itemize}
        \itemsep -4pt
        \item Created a educational video explaining the Wagner-Fischer spellcheck algorithm. \url{https://tinyurl.com/3krk4x46}
        \item Utilized the animation tool \textit{Manim} to create my video.
    \end{itemize}

    \textbf{Making Lane Detection Efficient for Autonomous Model Cars} \hfill Feb 2021 -- Jan 2023 \\
    Storrs, CT \\
    Mentors: Dr. Jinbo Bi, Dr. Shengli Zhou, Dr. Caiwen Ding, Dr. Fei Miao
    \begin{itemize}
        \itemsep -4pt
        \item Built and programmed autonomous model vehicles using AI and computer vision.
        \item Presented work at IEEE/ACM ISLPED.
    \end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
% SKILLS
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{2ex}} l }
    Languages: & Python, C, C\#, Java, HTML, JavaScript, TypeScript, React, LaTeX, SQL, PDDL, C++ \\
    Packages: & PyTorch, Torchvision, Tensorflow, Scikit-Learn, NetworkX, OpenCV, Gymnasium, NumPy, \\ & Matplotlib, Manim, SQLite\\ 
    Tools/Programs: & Linux, Windows, GitHub, VS Code, Visual Studio, Unity, Obsidian, Google Suite, \\ & Office Suite, Piazza, Desmos \\
    Certifications: & Forklift Trained and Certified \\
    \end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
% AWARDS
%----------------------------------------------------------------------------------------

\begin{rSection}{Awards \& Recognition}
    Honors Scholar \hfill 2023 -- Present \\
    CLAS Dean's List \hfill 2023 -- Present \\
    SoE Dean's List \hfill 2023 -- Present \\
    Babbige Scholar \hfill 2025 \\
    STEM Merit Scholarship ($\$5000$ per semester) \hfill 2023 -- Present \\
    2025 Babbige Scholar \hfill 2025 \\
    Global Citizen Scholarship \& Merit Scholarship ($\$500$ each) \hfill Sep 2024
\end{rSection}

%----------------------------------------------------------------------------------------
% ACTIVITIES
%----------------------------------------------------------------------------------------

\begin{rSection}{Activities}
    \textbf{Science Olympiad at UConn}, Treasurer \& Co-Founder \hfill Aug 2023 -- May 2026
    \begin{itemize}
        \itemsep -4pt
        \item Organized weekly meetings and workshops.
        \item Managed financials for the student organization.
        \item Led planning and execution of invitational competitions for high school and middle school teams.
    \end{itemize}

    \textbf{UConn Mathematics Club} \hfill Aug 2024 -- May 2026  
    \begin{itemize}
        \itemsep -4pt
        \item Attended weekly seminars led by faculty and graduate students.
    \end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
% RESEARCH INTERESTS
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Interests}
Artificial Intelligence, Machine Learning, Computer Vision, Robotics, Graph Theory, Algorithms
\end{rSection}

\end{document}
